A Digital Library for Crowds on the Real-Time Social Web

### 2011-05-05 docs/csce_675/paper.tex
Made minor modifications to paper.

Some other studies related come from areas like social network visualization,
short text visualization, progressive disclosure, and user modeling. Considering
social network visualization , studies like \cite{Boyd:2008} by Boyd et al described features
of on-line social networking sites and the history of the social networking sites,
and the changes during their developments.Deeper understanding of the social
networks can help boost the research in social network visualization. In Moreno's
following work \cite{Moreno:1953}, he emphasized the use of pictorial representations to map
social relations and the embedded patterns. He considered people as nodes in the
network and relations between people as the edges in the network.Laumann et al
\cite{Laumann:1966} applied computational procedure, multidimensional scaling to locate nodes in
visualizing network. The authors are also the first to plot the networks in three
dimensions. Other examples of good visualizations can be Facebook Friend Wheel
\cite{facebook_wheel} which visualizes a Facebook user's network of friends in a wheel format and
Trendsmap \cite{trends_map} which plots real time trending topics over two-dimensional (latitude,
longitude) world map, and you can zoom in to see the trending topics for a specific
location or an area.

@@

\begin{itemize}
  \item \noindent\textbf{Beanstalk}: Beanstalk is a simple, fast work queue. We use it to connect the crawlers, filters, and groupers together.
   \item \noindent\textbf{Tornado}: Tornado is an open source, non-blocking web server.  We choose it because it is fast and scalable.
   \item \noindent\textbf{MongoDB}: MongoDB is a scalable, high-performance, open source, document-oriented database. We store the crowds discovered by the framework in this DB. The API module interacts with this database to retrieve collections as required by the user query.
\end{itemize}

@@

{\scriptsize
 \bibliographystyle{abbrv}
 \bibliography{sigproc}
}
\balancecolumns % GM July 2000

>>>>

Some other studies related come from areas like social network visualization,
short text visualization, progressive disclosure, and user modeling. Considering
social network visualization , studies like \cite{Boyd:2008} by Boyd et al described features
of on-line social networking sites and the history of the social networking sites,
and the changes during their developments.Deeper understanding of the social
networks can help boost the research in social network visualization. In Moreno's
following work \cite{Moreno:1953}, he emphasized the use of pictorial representations to map
social relations and the embedded patterns. He considered people as nodes in the
network and relations between people as the edges in the network. Laumann et al
\cite{Laumann:1966} applied computational procedure, multidimensional scaling to locate nodes in
visualizing network. The authors are also the first to plot the networks in three
dimensions. Other examples of good visualizations can be Facebook Friend Wheel
\cite{facebook_wheel} which visualizes a Facebook user's network of friends in a wheel format and
Trendsmap \cite{trends_map} which plots real time trending topics over two-dimensional (latitude,
longitude) world map, and you can zoom in to see the trending topics for a specific
location or an area.

@@

\subsection{Tools}

The tool we used to develop this framework are as follows:
\begin{itemize}
 \item \noindent\textbf{PyLucene}: To provide the search functionality we use Apache Lucene. It provides methods for text indexing and searching. To integrate Lucene with our framework we use Pylucene which is a Python wrapper for Lucene. This is used in the filter module of our architecture.
 \item \noindent\textbf{CherryPy}: This is an object-oriented web framework for Python. The JSON REST API that interface the digital library with clients is hosted using this web framework.
 \item \noindent\textbf{NetworkX}: This is a library for manipulating graphs in Python. We use this to determine quality of crowds generated by crowd detection framework and filter out crowds of poor quality. This sits in the filter module.
  \item \noindent\textbf{Beanstalk}: Beanstalk is a simple, fast work queue. We use it to connect the crawlers, filters, and groupers together.
   \item \noindent\textbf{MongoDB}: MongoDB is a scalable, high-performance, open source, document-oriented database. We store the crowds discovered by the framework in this DB. The API module interacts with this database to retrieve collections as required by the user query.
\end{itemize}

@@

{
 \bibliographystyle{abbrv}
 \bibliography{sigproc}
}
\balancecolumns % GM July 2000
